Weak interspecific interactions in a sagebrush steppe: evidence from observations, models, and experiments

### 2017-01-31 removals/manuscript/removal_ms.tex
Fixed typos. This is the submitted version.

For recruitment in the IPM, the factor $ \Phi_j  = \exp{\left(\gamma_{j,t}^R +  \varphi_{jg}^R + \chi_{jm}^R + 
\left \langle \boldsymbol{\omega}^R , \boldsymbol{\sqrt{C'_{q,t}}} \right \rangle \right) }$
in eqn. (\ref{eqn:recrDataModel}) gives the expected 
area of new recruits per quadrat, per unit area of parents. To incorporate this recruitment function into the IPM, we assumed that individual fecundity increases linearly with individual area (equal to $e^u$ for a size-$u$ individual). The recruitment kernel is thus
$R_j(v_j,u_j,\vec{n})=c_{0,j}(v_j)e^{u_j}\Phi_j$ \citep{adler_coexistence_2010} where $c_{0,j}$ is the
size distribution of new recruits. $\Phi_j$ is calculated from eqn. (\ref{eqn:recrDataModel}) with total cover values computed from the population densities as $C'_{j,t} = \int e^u n(u_{j,t}) du$.

We simulated the IPM to estimate equilibrium abundances under three different scenarios. For all IPM simulations, we set the spatial random effects to zero, meaning that we are simulating dynamics on a hypothetical, average site. The first scenario featured all four species and our ``baseline'' model for control plots (no removal effects). We initialized all species with arbitrarily low cover and ran the model for 500 time steps (years) to allow the community to reach an equilibrium. To incorporate temporal environmental variation, at each time step we randomly selected one of the 30 sets of random year effects for the survival, growth and recruitment models (``kernel selection'' in the terminology of \citealt{metcalf_statistical_2015}). We calculated the equilibrium cover for each species by simulating an additional 2000 time steps and averaging each species' cover over this period. For the second scenario, we set the cover of \textit{A. tripartita} to zero and then repeated the procedure. This simulation estimates the competitive release of grasses following \textit{A. tripartita} removal according to the baseline model (no removal effects). For the third scenario, we again set  \textit{A. triparitia} cover to zero, but this time we projected the model using the vital rate regressions that include removal effects. If our baseline model successfully predicts competitive release observed in the removal experiment, then the results of the second and third scenarios should be similar. To the extent that the baseline model underestimates (or overestimates) the actual competitive release, the results of the second and third scenarios will differ. As with the IBM, we repeated these simulations using maximum removal treatment effects represented by parameters values at the 5\% or 95\% confidence limit farthest from zero. We did not simulate long-term \textit{A. tripartita} response to grass removal because the vital rate regressions for \textit{A. tripartita} showed that the baseline model effectively predicted removal effects.

@@

Finally, we evaluated pre-existing differences in community composition in removal and control plots. In selecting removal plots, our criteria required candidate plots to include at least a certain amount of our target removal species. Because we adopted the historical plots as our controls, the same criteria were not applied (a control plot might not contain any \textit{A. tripartita}). To quantify resulting differences in pre-treatment (2011) composition, we compared neighborhood crowding at the individual plant level (the $\boldsymbol{W}$ of the growth regression) across treatments. \textit{A. tripartita} crowding and crowding by all subdominant shrub and grass species appeared greater in removal plots than in the controls, whereas crowding by \textit{H. comata} was lower in removals than controls, though it was absent from most \textit{P. spicata} neighborhoods in both treatments (Fig. \ref{fig:W-by-treatment}). These pre-existing differences in composition raise the possibility that plots selected for the removal treatments might differ from the control plots in some unobserved covariate that could influence plant performance.

@@

  \begin{figure}[tbp]
  \centering
  \includegraphics[width=1\textwidth]{cover_change_1to1}
  \caption{Comparison of observed and predicted annual per capita growth rates across species in (A) control and (B) removal treatments. The black line is a 1:1 line. Solid symbols correspond to predictions form the baseline IBM (no removal effects) and open symbols in (B) show predictions from an IBM that includes removal treatment effects. Source file: \texttt{ibm\textbackslash summarize\textunderscore sims1step.r}. }
  \label{fig:ObsPred1to1}
  \end{figure}

@@

 The equilibrium cover of \textit{A. tripartita} simulated by the IPM (6.0\%) is consistent with observed cover during the historical data collection period (6.6\% from 1931-1956), but is low compared to contemporary observed cover (15-25\%, Fig. \ref{fig:CoverTrends}). Could the small competitive release following simulated \textit{A. tripartita} removal simply reflect the low \textit{A. tripartita} cover? To explore this possibility, we increased \text{Artemisia} cover in the baseline simulation by increasing average \textit{A. tripartita} fecundity. The increased fecundity led to a doubling of \textit{A. tripartita} average cover, but had essentially zero effect on the cover of the grasses (changes of less than 0.1\% cover).

@@

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:33:00 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{H. comata} survival model (see Table \ref{ARTRsurvival} for an explanation of coefficient names
and column headers).} 
\label{HECOsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 1.4189 & 0.2115 & 0.9991 & 1.4190 & 1.8371 & 1.4192 & 0.0000 \\ 
  logarea & 1.2885 & 0.0813 & 1.1399 & 1.2843 & 1.4601 & 1.2758 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.3958 & 0.4175 & -0.4193 & 0.3942 & 1.2190 & 0.3909 & 0.0000 \\ 
  W.ARTR & -0.0064 & 0.0028 & -0.0120 & -0.0064 & -0.0009 & -0.0064 & 0.0000 \\ 
  W.HECO & -0.6647 & 0.0673 & -0.7996 & -0.6638 & -0.5351 & -0.6619 & 0.0000 \\ 
  W.POSE & 0.0732 & 0.0534 & -0.0304 & 0.0728 & 0.1790 & 0.0720 & 0.0000 \\ 
  W.PSSP & 0.0190 & 0.0184 & -0.0167 & 0.0188 & 0.0554 & 0.0185 & 0.0000 \\ 
  W.allcov & 0.0021 & 0.0047 & -0.0072 & 0.0021 & 0.0113 & 0.0021 & 0.0000 \\ 
  W.allpts & -0.1185 & 0.0919 & -0.2998 & -0.1183 & 0.0610 & -0.1177 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:34:30 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{P. secunda} survival model (see Table \ref{ARTRsurvival} for an explanation of coefficient names
and column headers).} 
\label{POSEsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 1.3162 & 0.1965 & 0.9242 & 1.3171 & 1.7024 & 1.3186 & 0.0000 \\ 
  logarea & 1.0585 & 0.0640 & 0.9365 & 1.0569 & 1.1902 & 1.0537 & 0.0000 \\ 
  TreatmentNo\_shrub & -0.2572 & 0.1723 & -0.5949 & -0.2573 & 0.0811 & -0.2576 & 0.0000 \\ 
  W.ARTR & 0.0001 & 0.0019 & -0.0036 & 0.0001 & 0.0038 & 0.0001 & 0.0000 \\ 
  W.HECO & -0.0153 & 0.0138 & -0.0424 & -0.0154 & 0.0119 & -0.0154 & 0.0000 \\ 
  W.POSE & -1.2632 & 0.0816 & -1.4260 & -1.2623 & -1.1053 & -1.2605 & 0.0000 \\ 
  W.PSSP & 0.0249 & 0.0122 & 0.0011 & 0.0249 & 0.0490 & 0.0247 & 0.0000 \\ 
  W.allcov & -0.0024 & 0.0026 & -0.0075 & -0.0024 & 0.0029 & -0.0024 & 0.0000 \\ 
  W.allpts & 0.0018 & 0.0524 & -0.1009 & 0.0018 & 0.1048 & 0.0017 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:35:48 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{P. spicata} survival model (see Table \ref{ARTRsurvival} for an explanation of coefficient names
and column headers).} 
\label{PSSPsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 1.2121 & 0.1699 & 0.8815 & 1.2103 & 1.5533 & 1.2066 & 0.0000 \\ 
  logarea & 1.5492 & 0.0976 & 1.3612 & 1.5474 & 1.7473 & 1.5437 & 0.0000 \\ 
  TreatmentNo\_shrub & -0.1885 & 0.2208 & -0.6237 & -0.1879 & 0.2431 & -0.1867 & 0.0000 \\ 
  W.ARTR & 0.0101 & 0.0021 & 0.0061 & 0.0101 & 0.0142 & 0.0101 & 0.0000 \\ 
  W.HECO & 0.0046 & 0.0185 & -0.0319 & 0.0046 & 0.0406 & 0.0047 & 0.0000 \\ 
  W.POSE & 0.0245 & 0.0384 & -0.0502 & 0.0242 & 0.1007 & 0.0236 & 0.0000 \\ 
  W.PSSP & -0.4430 & 0.0291 & -0.5010 & -0.4427 & -0.3867 & -0.4420 & 0.0000 \\ 
  W.allcov & 0.0100 & 0.0028 & 0.0046 & 0.0100 & 0.0155 & 0.0100 & 0.0000 \\ 
  W.allpts & 0.0943 & 0.0605 & -0.0246 & 0.0944 & 0.2129 & 0.0944 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

@@

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:36:24 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{H. comata} growth model (see Table \ref{ARTRgrowth} for an explanation of coefficient names
and column headers).} 
\label{HECOgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.3782 & 0.0797 & 0.2212 & 0.3783 & 0.5343 & 0.3784 & 0.0000 \\ 
  logarea.t0 & 0.8272 & 0.0205 & 0.7869 & 0.8272 & 0.8674 & 0.8272 & 0.0000 \\ 
  TreatmentNo\_shrub & -0.0162 & 0.1336 & -0.2785 & -0.0162 & 0.2460 & -0.0162 & 0.0000 \\ 
  W.ARTR & -0.0031 & 0.0010 & -0.0051 & -0.0031 & -0.0010 & -0.0031 & 0.0000 \\ 
  W.HECO & -0.0479 & 0.0195 & -0.0862 & -0.0479 & -0.0098 & -0.0479 & 0.0000 \\ 
  W.POSE & 0.0242 & 0.0162 & -0.0077 & 0.0242 & 0.0560 & 0.0242 & 0.0000 \\ 
  W.PSSP & -0.0151 & 0.0065 & -0.0279 & -0.0151 & -0.0023 & -0.0151 & 0.0000 \\ 
  W.allcov & -0.0038 & 0.0019 & -0.0076 & -0.0038 & 0.0000 & -0.0038 & 0.0000 \\ 
  W.allpts & -0.0513 & 0.0380 & -0.1258 & -0.0513 & 0.0232 & -0.0513 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:36:58 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{P. secunda} growth model (see Table \ref{ARTRgrowth} for an explanation of coefficient names
and column headers).} 
\label{POSEgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.4923 & 0.0681 & 0.3581 & 0.4923 & 0.6259 & 0.4924 & 0.0000 \\ 
  logarea.t0 & 0.6750 & 0.0232 & 0.6292 & 0.6750 & 0.7203 & 0.6751 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.2161 & 0.0644 & 0.0897 & 0.2161 & 0.3425 & 0.2161 & 0.0000 \\ 
  W.ARTR & -0.0002 & 0.0008 & -0.0019 & -0.0002 & 0.0014 & -0.0002 & 0.0000 \\ 
  W.HECO & 0.0039 & 0.0063 & -0.0084 & 0.0039 & 0.0161 & 0.0039 & 0.0000 \\ 
  W.POSE & -0.2641 & 0.0387 & -0.3400 & -0.2641 & -0.1883 & -0.2641 & 0.0000 \\ 
  W.PSSP & -0.0073 & 0.0056 & -0.0183 & -0.0073 & 0.0038 & -0.0073 & 0.0000 \\ 
  W.allcov & -0.0003 & 0.0012 & -0.0026 & -0.0003 & 0.0020 & -0.0003 & 0.0000 \\ 
  W.allpts & -0.0254 & 0.0231 & -0.0709 & -0.0254 & 0.0200 & -0.0254 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:37:48 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{P. spicata} growth model (see Table \ref{ARTRgrowth} for an explanation of coefficient names
and column headers).} 
\label{PSSPgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.3987 & 0.0660 & 0.2690 & 0.3987 & 0.5281 & 0.3988 & 0.0000 \\ 
  logarea.t0 & 0.8249 & 0.0149 & 0.7956 & 0.8249 & 0.8543 & 0.8249 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.1948 & 0.0714 & 0.0546 & 0.1948 & 0.3349 & 0.1948 & 0.0000 \\ 
  W.ARTR & -0.0025 & 0.0008 & -0.0041 & -0.0025 & -0.0010 & -0.0025 & 0.0000 \\ 
  W.HECO & -0.0118 & 0.0072 & -0.0260 & -0.0118 & 0.0023 & -0.0118 & 0.0000 \\ 
  W.POSE & -0.0067 & 0.0130 & -0.0323 & -0.0067 & 0.0189 & -0.0067 & 0.0000 \\ 
  W.PSSP & -0.1480 & 0.0133 & -0.1740 & -0.1480 & -0.1220 & -0.1480 & 0.0000 \\ 
  W.allcov & -0.0036 & 0.0011 & -0.0057 & -0.0036 & -0.0015 & -0.0036 & 0.0000 \\ 
  W.allpts & -0.0522 & 0.0236 & -0.0984 & -0.0522 & -0.0060 & -0.0522 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Summary of fixed effects for the \textit{P. secunda} growth model with individual-level \textit{A. tripartita removal} data (the ``inARTR" coefficient). See Table \ref{ARTRgrowth} for an explanation of other coefficient names and column headers). } 
\label{table:POSEgrowth-inARTR}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.4932 & 0.0622 & 0.3700 & 0.4934 & 0.6154 & 0.4937 & 0.0000 \\ 
  logarea.t0 & 0.6746 & 0.0220 & 0.6306 & 0.6747 & 0.7177 & 0.6750 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.2370 & 0.0739 & 0.0919 & 0.2370 & 0.3820 & 0.2370 & 0.0000 \\ 
  W.ARTR & -0.0002 & 0.0008 & -0.0018 & -0.0002 & 0.0014 & -0.0002 & 0.0000 \\ 
  W.HECO & 0.0038 & 0.0062 & -0.0083 & 0.0038 & 0.0160 & 0.0038 & 0.0000 \\ 
  W.POSE & -0.2644 & 0.0383 & -0.3395 & -0.2644 & -0.1893 & -0.2644 & 0.0000 \\ 
  W.PSSP & -0.0075 & 0.0056 & -0.0184 & -0.0075 & 0.0034 & -0.0075 & 0.0000 \\ 
  W.allcov & -0.0003 & 0.0012 & -0.0026 & -0.0003 & 0.0020 & -0.0003 & 0.0000 \\ 
  W.allpts & -0.0258 & 0.0229 & -0.0707 & -0.0258 & 0.0191 & -0.0258 & 0.0000 \\ 
  inARTR & -0.0592 & 0.1133 & -0.2817 & -0.0592 & 0.1632 & -0.0592 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

For recruitment in the IPM, the factor $ \Phi_j  =\exp{\left(\gamma_{j,t}^R +  \varphi_{jg}^R + \chi_{jh}^R + 
\sum \limits_{m} \omega_{jm}^R \sqrt{C'_{mq,t}} \right)}$
in eqn. (\ref{eqn:recrDataModel}) gives the expected 
area of new recruits per quadrat, per unit area of parents. To incorporate this recruitment function into the IPM, we assumed that individual fecundity increases linearly with individual area (equal to $e^u$ for a size-$u$ individual). The recruitment kernel is thus
$R_j(v_j,u_j,\vec{n})=c_{0,j}(v_j)e^{u_j}\Phi_j$ \citep{adler_coexistence_2010} where $c_{0,j}$ is the
size distribution of new recruits. $\Phi_j$ is calculated from eqn. (\ref{eqn:recrDataModel}) with total cover values computed from the population densities as $C'_{j,t} = \int e^u n(u_{j,t}) du$.

We simulated the IPM to estimate equilibrium abundances under three different scenarios. For all IPM simulations, we set the spatial random effects to zero, meaning that we are simulating dynamics on a hypothetical, average site. The first scenario featured all four species and our ``baseline'' model for control plots (no removal effects). We initialized all species with arbitrarily low cover and ran the model for 500 time steps (years) to allow the community to reach an equilibrium. To incorporate temporal environmental variation, at each time step we randomly selected one of the 30 sets of random year effects for the survival, growth and recruitment models (``kernel selection'' in the terminology of \citealt{metcalf_statistical_2015}). We calculated the equilibrium cover for each species by simulating an additional 2000 time steps and averaging each species' cover over this period. For the second scenario, we set the cover of \textit{A. tripartita} to zero and then repeated the procedure. This simulation estimates the competitive release of grasses following \textit{A. tripartita} removal according to the baseline model (no removal effects). For the third scenario, we again set  \textit{A. triparitia} cover to zero, but this time we projected the model using the vital rate regressions that include removal effects. If our baseline model successfully predicts competitive release observed in the removal experiment, then the results of the second and third scenarios should be similar. To the extent that the baseline model underestimates (or overestimates) the actual competitive release, the results of the second and third scenarios will differ. As with the IBM, we repeated these simulations using maximum removal treatment effects represented by parameters values at the 5\% or 95\% confidence limit farthest from zero. We did not simulate long-term \textit{A. tripartita} response to grass removal because the removal treatment effects in the vital rate regressions were never significantly different from zero, indicating that the baseline model effectively predicted competitive release.

@@

Finally, we evaluated pre-existing differences in community composition in removal and control plots. In selecting removal plots, our criteria required candidate plots to include at least a certain amount of our target removal species. Because we adopted the historical plots as our controls, the same criteria were not applied (a control plot might not contain any \textit{A. tripartita}). To quantify resulting differences in pre-treatment (2011) composition, we compared neighborhood crowding at the individual plant level (the $W_{jm}$'s of the growth regressions) across treatments. \textit{A. tripartita} crowding and crowding by all subdominant shrub and grass species appeared greater in removal plots than in the controls, whereas crowding by \textit{H. comata} was lower in removals than controls, though it was absent from most \textit{P. spicata} neighborhoods in both treatments (Fig. \ref{fig:W-by-treatment}). These pre-existing differences in composition raise the possibility that plots selected for the removal treatments might differ from the control plots in some unobserved covariate that could influence plant performance.

@@

  \begin{figure}[tbp]
  \centering
  \includegraphics[width=1\textwidth]{cover_change_1to1}
  \caption{Comparison of observed and predicted annual per capita growth rates across species in (A) control and (B) removal treatments. The black line is a 1:1 line. Solid symbols correspond to predictions from the baseline IBM (no removal effects) and open symbols in (B) show predictions from an IBM that includes removal treatment effects. Source file: \texttt{ibm\textbackslash summarize\textunderscore sims1step.r}. }
  \label{fig:ObsPred1to1}
  \end{figure}

@@

 The equilibrium cover of \textit{A. tripartita} simulated by the IPM (6.0\%) is consistent with observed cover during the historical data collection period (6.6\% from 1931-1956), but is low compared to contemporary observed cover (15-25\%, Fig. \ref{fig:CoverTrends}). Could the small competitive release following simulated \textit{A. tripartita} removal simply reflect the low \textit{A. tripartita} cover? To explore this possibility, we increased \textit{A. tripartita} cover in the baseline simulation by increasing average \textit{A. tripartita} fecundity. The increased fecundity led to a doubling of \textit{A. tripartita} average cover, but had essentially zero effect on the cover of the grasses (changes of less than 0.1\% cover).

@@

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:33:00 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{H. comata} survival model. See Table \ref{ARTRsurvival} for an explanation of coefficient names
and column headers.} 
\label{HECOsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 1.4189 & 0.2115 & 0.9991 & 1.4190 & 1.8371 & 1.4192 & 0.0000 \\ 
  logarea & 1.2885 & 0.0813 & 1.1399 & 1.2843 & 1.4601 & 1.2758 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.3958 & 0.4175 & -0.4193 & 0.3942 & 1.2190 & 0.3909 & 0.0000 \\ 
  W.ARTR & -0.0064 & 0.0028 & -0.0120 & -0.0064 & -0.0009 & -0.0064 & 0.0000 \\ 
  W.HECO & -0.6647 & 0.0673 & -0.7996 & -0.6638 & -0.5351 & -0.6619 & 0.0000 \\ 
  W.POSE & 0.0732 & 0.0534 & -0.0304 & 0.0728 & 0.1790 & 0.0720 & 0.0000 \\ 
  W.PSSP & 0.0190 & 0.0184 & -0.0167 & 0.0188 & 0.0554 & 0.0185 & 0.0000 \\ 
  W.allcov & 0.0021 & 0.0047 & -0.0072 & 0.0021 & 0.0113 & 0.0021 & 0.0000 \\ 
  W.allpts & -0.1185 & 0.0919 & -0.2998 & -0.1183 & 0.0610 & -0.1177 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:34:30 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{P. secunda} survival model. See Table \ref{ARTRsurvival} for an explanation of coefficient names
and column headers.} 
\label{POSEsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 1.3162 & 0.1965 & 0.9242 & 1.3171 & 1.7024 & 1.3186 & 0.0000 \\ 
  logarea & 1.0585 & 0.0640 & 0.9365 & 1.0569 & 1.1902 & 1.0537 & 0.0000 \\ 
  TreatmentNo\_shrub & -0.2572 & 0.1723 & -0.5949 & -0.2573 & 0.0811 & -0.2576 & 0.0000 \\ 
  W.ARTR & 0.0001 & 0.0019 & -0.0036 & 0.0001 & 0.0038 & 0.0001 & 0.0000 \\ 
  W.HECO & -0.0153 & 0.0138 & -0.0424 & -0.0154 & 0.0119 & -0.0154 & 0.0000 \\ 
  W.POSE & -1.2632 & 0.0816 & -1.4260 & -1.2623 & -1.1053 & -1.2605 & 0.0000 \\ 
  W.PSSP & 0.0249 & 0.0122 & 0.0011 & 0.0249 & 0.0490 & 0.0247 & 0.0000 \\ 
  W.allcov & -0.0024 & 0.0026 & -0.0075 & -0.0024 & 0.0029 & -0.0024 & 0.0000 \\ 
  W.allpts & 0.0018 & 0.0524 & -0.1009 & 0.0018 & 0.1048 & 0.0017 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:35:48 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{P. spicata} survival model. See Table \ref{ARTRsurvival} for an explanation of coefficient names
and column headers.} 
\label{PSSPsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 1.2121 & 0.1699 & 0.8815 & 1.2103 & 1.5533 & 1.2066 & 0.0000 \\ 
  logarea & 1.5492 & 0.0976 & 1.3612 & 1.5474 & 1.7473 & 1.5437 & 0.0000 \\ 
  TreatmentNo\_shrub & -0.1885 & 0.2208 & -0.6237 & -0.1879 & 0.2431 & -0.1867 & 0.0000 \\ 
  W.ARTR & 0.0101 & 0.0021 & 0.0061 & 0.0101 & 0.0142 & 0.0101 & 0.0000 \\ 
  W.HECO & 0.0046 & 0.0185 & -0.0319 & 0.0046 & 0.0406 & 0.0047 & 0.0000 \\ 
  W.POSE & 0.0245 & 0.0384 & -0.0502 & 0.0242 & 0.1007 & 0.0236 & 0.0000 \\ 
  W.PSSP & -0.4430 & 0.0291 & -0.5010 & -0.4427 & -0.3867 & -0.4420 & 0.0000 \\ 
  W.allcov & 0.0100 & 0.0028 & 0.0046 & 0.0100 & 0.0155 & 0.0100 & 0.0000 \\ 
  W.allpts & 0.0943 & 0.0605 & -0.0246 & 0.0944 & 0.2129 & 0.0944 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

@@

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:36:24 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{H. comata} growth model. See Table \ref{ARTRgrowth} for an explanation of coefficient names
and column headers.} 
\label{HECOgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.3782 & 0.0797 & 0.2212 & 0.3783 & 0.5343 & 0.3784 & 0.0000 \\ 
  logarea.t0 & 0.8272 & 0.0205 & 0.7869 & 0.8272 & 0.8674 & 0.8272 & 0.0000 \\ 
  TreatmentNo\_shrub & -0.0162 & 0.1336 & -0.2785 & -0.0162 & 0.2460 & -0.0162 & 0.0000 \\ 
  W.ARTR & -0.0031 & 0.0010 & -0.0051 & -0.0031 & -0.0010 & -0.0031 & 0.0000 \\ 
  W.HECO & -0.0479 & 0.0195 & -0.0862 & -0.0479 & -0.0098 & -0.0479 & 0.0000 \\ 
  W.POSE & 0.0242 & 0.0162 & -0.0077 & 0.0242 & 0.0560 & 0.0242 & 0.0000 \\ 
  W.PSSP & -0.0151 & 0.0065 & -0.0279 & -0.0151 & -0.0023 & -0.0151 & 0.0000 \\ 
  W.allcov & -0.0038 & 0.0019 & -0.0076 & -0.0038 & 0.0000 & -0.0038 & 0.0000 \\ 
  W.allpts & -0.0513 & 0.0380 & -0.1258 & -0.0513 & 0.0232 & -0.0513 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:36:58 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{P. secunda} growth model. See Table \ref{ARTRgrowth} for an explanation of coefficient names
and column headers.} 
\label{POSEgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.4923 & 0.0681 & 0.3581 & 0.4923 & 0.6259 & 0.4924 & 0.0000 \\ 
  logarea.t0 & 0.6750 & 0.0232 & 0.6292 & 0.6750 & 0.7203 & 0.6751 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.2161 & 0.0644 & 0.0897 & 0.2161 & 0.3425 & 0.2161 & 0.0000 \\ 
  W.ARTR & -0.0002 & 0.0008 & -0.0019 & -0.0002 & 0.0014 & -0.0002 & 0.0000 \\ 
  W.HECO & 0.0039 & 0.0063 & -0.0084 & 0.0039 & 0.0161 & 0.0039 & 0.0000 \\ 
  W.POSE & -0.2641 & 0.0387 & -0.3400 & -0.2641 & -0.1883 & -0.2641 & 0.0000 \\ 
  W.PSSP & -0.0073 & 0.0056 & -0.0183 & -0.0073 & 0.0038 & -0.0073 & 0.0000 \\ 
  W.allcov & -0.0003 & 0.0012 & -0.0026 & -0.0003 & 0.0020 & -0.0003 & 0.0000 \\ 
  W.allpts & -0.0254 & 0.0231 & -0.0709 & -0.0254 & 0.0200 & -0.0254 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:37:48 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{P. spicata} growth model. See Table \ref{ARTRgrowth} for an explanation of coefficient names
and column headers.} 
\label{PSSPgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.3987 & 0.0660 & 0.2690 & 0.3987 & 0.5281 & 0.3988 & 0.0000 \\ 
  logarea.t0 & 0.8249 & 0.0149 & 0.7956 & 0.8249 & 0.8543 & 0.8249 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.1948 & 0.0714 & 0.0546 & 0.1948 & 0.3349 & 0.1948 & 0.0000 \\ 
  W.ARTR & -0.0025 & 0.0008 & -0.0041 & -0.0025 & -0.0010 & -0.0025 & 0.0000 \\ 
  W.HECO & -0.0118 & 0.0072 & -0.0260 & -0.0118 & 0.0023 & -0.0118 & 0.0000 \\ 
  W.POSE & -0.0067 & 0.0130 & -0.0323 & -0.0067 & 0.0189 & -0.0067 & 0.0000 \\ 
  W.PSSP & -0.1480 & 0.0133 & -0.1740 & -0.1480 & -0.1220 & -0.1480 & 0.0000 \\ 
  W.allcov & -0.0036 & 0.0011 & -0.0057 & -0.0036 & -0.0015 & -0.0036 & 0.0000 \\ 
  W.allpts & -0.0522 & 0.0236 & -0.0984 & -0.0522 & -0.0060 & -0.0522 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Summary of fixed effects for the \textit{P. secunda} growth model with individual-level \textit{A. tripartita removal} data (the ``inARTR" coefficient). See Table \ref{ARTRgrowth} for an explanation of other coefficient names and column headers. } 
\label{table:POSEgrowth-inARTR}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.4932 & 0.0622 & 0.3700 & 0.4934 & 0.6154 & 0.4937 & 0.0000 \\ 
  logarea.t0 & 0.6746 & 0.0220 & 0.6306 & 0.6747 & 0.7177 & 0.6750 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.2370 & 0.0739 & 0.0919 & 0.2370 & 0.3820 & 0.2370 & 0.0000 \\ 
  W.ARTR & -0.0002 & 0.0008 & -0.0018 & -0.0002 & 0.0014 & -0.0002 & 0.0000 \\ 
  W.HECO & 0.0038 & 0.0062 & -0.0083 & 0.0038 & 0.0160 & 0.0038 & 0.0000 \\ 
  W.POSE & -0.2644 & 0.0383 & -0.3395 & -0.2644 & -0.1893 & -0.2644 & 0.0000 \\ 
  W.PSSP & -0.0075 & 0.0056 & -0.0184 & -0.0075 & 0.0034 & -0.0075 & 0.0000 \\ 
  W.allcov & -0.0003 & 0.0012 & -0.0026 & -0.0003 & 0.0020 & -0.0003 & 0.0000 \\ 
  W.allpts & -0.0258 & 0.0229 & -0.0707 & -0.0258 & 0.0191 & -0.0258 & 0.0000 \\ 
  inARTR & -0.0592 & 0.1133 & -0.2817 & -0.0592 & 0.1632 & -0.0592 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}
